---
title: Logistic regression
author: Kwang-Yeol Park
date: '2019-06-28'
slug: logistic-regression
categories:
  - R
tags:
  - statistics
---
## Binary logistic regression

### Youtube video

```{r echo=FALSE}
# blogdown::shortcode("youtube", "BIkmggffG9w")
blogdown::shortcode("youtube", "Vak6Oat2Z88")
```

### Linear regression
- Background
  + ordinary least squares

### Logistic regerssion
- Background
  + logistic function
  + maximum likelihood method
  + odds and odds ratio

- Interpretation of coefficient

- Exercise: R
  + R data manipulation
    - factor
    - dplyr
  + descriptive
  + simple logistic regression
  + multivariable logistic regression
  
  <!-- + multi-collinearity: vif() -->
  
  

## Ordinal logistic regression

### Youtube video

```{r echo=FALSE}
blogdown::shortcode("youtube", "nNFGbJW6_Ds")
# blogdown::shortcode("youtube", "Vak6Oat2Z88")
```

### Example

### Ordinal logistic regression
- Underlying assumptions
  + proportional odds assumption
  
- Exercise: R